Community Detection in the Setting of Generalized Random Dot Product Graphs

### 2023-01-13 slides/slides.Rmd
tried to make a plot prettier

1. Draw $z_1, ..., z_n \iid \Multinomial(1/2, 1/2)$.
2. Draw $t_1, ..., t_n \iid \Uniform(0, 1)$. 
3. Let each $x_i = g_{z_i}(t_i)$ where  $g_1(t) = [ t^2, 2 t (1-t) ]^\top$ and $g_2(t) = [ 2 t (1-t), (1-t)^2 ]^\top$. 
Collect the latent vectors into matrix $X = [ x_1 \mid \cdots \mid x_n ]^\top$. 
4. Draw $A \sim \GRDPG_{2,0}(X)$ .

@@

1. Draw $z_1, ..., z_n \iid \Multinomial(1/3, 1/3, 1/3)$.
2. Draw $t_1, ..., t_n \iid \Uniform(0, 1)$. 
3. Let each $x_i = g_{z_i}(t_i)$ where
    i. $g_1(t) = [ 2 t (t-1), t^2, 0 ]^\top$
    ii. $g_2(t) = [ 0, t^2, 2 t (t-1) ]^\top$
    iii. $g_3(t) = [2 t (t-1), t^2, 2 t (t-1) ]^\top$.
4. Collect the latent vectors into matrix $X = [ x_1 \mid \cdots \mid x_n ]^\top$.
5. Draw $A \sim \GRDPG_{3,0}(X)$.

```{r three-curves, cache = TRUE, fig.height = 4, fig.width = 15, fig.cap = 'Latent vectors (left) and ASE (right) of one realization of the mixture model in the simulation setup with $K=3$ manifolds.', out.width = '100%'}
par(mfrow = c(1, 2))

@@

1. Draw $z_1, ..., z_n \iid \Multinomial(1/3, 1/3, 1/3)$.
2. Draw $t_1, ..., t_n \iid \Uniform(0, 1)$. 
3. Let each $x_i = g_{z_i}(t_i)$ where
    i. $g_1(t) = [ 2 t (t-1), t^2, 0 ]^\top$
    ii. $g_2(t) = [ 0, t^2, 2 t (t-1) ]^\top$
    iii. $g_3(t) = [2 t (t-1), t^2, 2 t (t-1) ]^\top$.
4. Collect the latent vectors into matrix $X = [ x_1 \mid \cdots \mid x_n ]^\top$.
5. Draw $A \sim \GRDPG_{3,0}(X)$.

>>>>

1. Draw $z_1, ..., z_n \iid \Categorical(1/2, 1/2)$.
2. Draw $t_1, ..., t_n \iid \Uniform(0, 1)$. 
3. Let each $x_i = g_{z_i}(t_i)$ where  $g_1(t) = [ t^2, 2 t (1-t) ]^\top$ and $g_2(t) = [ 2 t (1-t), (1-t)^2 ]^\top$. 
Collect the latent vectors into matrix $X = [ x_1 \mid \cdots \mid x_n ]^\top$. 
4. Draw $A \sim \GRDPG_{2,0}(X)$ .

@@

1. Draw $z_1, ..., z_n \iid \Categorical(1/3, 1/3, 1/3)$.
2. Draw $t_1, ..., t_n \iid \Uniform(0, 1)$. 
3. Let each $x_i = g_{z_i}(t_i)$ where
    i. $g_1(t) = [ 2 t (t-1), t^2, 0 ]^\top$
    ii. $g_2(t) = [ 0, t^2, 2 t (t-1) ]^\top$
    iii. $g_3(t) = [2 t (t-1), t^2, 2 t (t-1) ]^\top$.
4. Collect the latent vectors into matrix $X = [ x_1 \mid \cdots \mid x_n ]^\top$.
5. Draw $A \sim \GRDPG_{3,0}(X)$.

```{r three-curves, cache = TRUE, fig.height = 4, fig.width = 15, fig.cap = 'Latent vectors (left) and ASE (right) of one realization of the mixture model in the simulation setup with $K=3$ manifolds.', out.width = '100%'}
par(mfrow = c(1, 2), mar = c(0, 0, 0, 0))

@@

1. Draw $z_1, ..., z_n \iid \Categorical(1/3, 1/3, 1/3)$.
2. Draw $t_1, ..., t_n \iid \Uniform(0, 1)$. 
3. Let each $x_i = g_{z_i}(t_i)$ where
    i. $g_1(t) = [ 2 t (t-1), t^2, 0 ]^\top$
    ii. $g_2(t) = [ 0, t^2, 2 t (t-1) ]^\top$
    iii. $g_3(t) = [2 t (t-1), t^2, 2 t (t-1) ]^\top$.
4. Collect the latent vectors into matrix $X = [ x_1 \mid \cdots \mid x_n ]^\top$.
5. Draw $A \sim \GRDPG_{3,0}(X)$.
